Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-07 draft.tex
more swiss cheese

\begin{thm}
\label{T:En=Fac} 
There is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant prefactorization algebras on~$\RR^n$. 
\end{thm}

@@

Given an $E_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
This $\infty$-category is obtained by ``forgetting" the $E_{n+1}$-algebra to an $E_1$-algebra and then taking the left-modules for this $E_1$-algebra.

The operad of little $n$-disks is built from configurations of disjoint unions of $n$-disks inside $n$-dimensional Euclidean space.
There is a similar operadic picture which encodes $E_{n+1}$-algebras together with their left-modules. 
The idea is too look at configurations of disks and half-disks inside of the upper-half space $\HH^{n+1} = \{(x_1,\ldots, x_{n+1}) \; | \; x_{n+1} \geq 0\}$. 
What results is a two-colored operad known as the $(n+1)$-dimensional Swiss cheese operad where the two colors correspond to disks and half-disks.

An algebra over this colored operad can be identified with a pair of objects $(B,M)$ where $B$ is an $E_{n+1}$-algebra and $M$ is an $E_n$-algebra in the category of left $B$-modules.
Indeed, if one restricts to the ``disk" colors we recover the data of $B$. 
The operadic structure maps which include disks and half-disks embedded inside bigger half-disks encodes the left-module structure of $A$ on $B$.

Given an $E_n$-algebra $A$ we know that $E_n$-center $\fZ_n(A)$ has the structure of an $E_{n+1}$ algebra.
Moreover, the pair $(\fZ_{n} (A), A)$ can be given the structure of an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
In fact, $(\fZ_{n} (A), A)$ is the {\em universal} such pair.
This universality is a conjecture of \cite{Kontsevich} which was later made precise and proved in \cite{Thomas, Tamarkin, Dolgushev, jnkf others?}. 
One consequence of this \brian{universal property}

Abstractly, an algebra over the $(n+1)$-dimensional Swiss cheese operad can be modeled as a {\em constructible} factorization algebra on the upper half space $\HH^{n+1}$. 
Concretely, this is the data of a pair $(\bB, \bM)$ where $\bB$ is a locally constant factorization algebra on the ``bulk" manifold $\RR^n \times \RR_{>0}$ and $\bM$ is a locally constant factorization algebra on the boundary $\RR^n \times \{0\}$.

\begin{prp}[\cite{Lurie, AF}]
For any smooth manifold $M$ and Lie algebra $\fg$ there exists a constructible factorization algebra on $M \times \RR_{\geq 0}$ which is a model for the algebra $(\fZ_n(\fg), \UU_n(\fg))$ over the $(n+1)$-dimensional Swiss cheese operad.
\end{prp}

@@

Given an $E_n$-algebra $A$ the pair $(\fZ_n (A) , A)$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
The first objective is to define a certain ``classical limit" of this pair in the case that $A$ is an $E_n$-enveloping algebra.

@@

The key insight is that there exists a filtration on our model for the $E_n$-center $\bZ_n(\fg)$ and the $E_n$-enveloping algebra $\bU_n (\fg)$ whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are {\em commutative} factorization algebras.

\brian{additivity}

@@

The associated graded pair in Proposition \ref{prp:swiss1} carries the additional Poisson-type structure.

@@

A constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a pair of factorization algebras $(\pi_* \bA , \bA_{\partial})$ on $M$ which locally define the $E_1$-model for $(n+1)$-Swiss cheese algebras.

The next goal of this section is to provide a model of the classical limit of the $E_n$-center as a constructible factorization algebra.

@@

We accomplish Proposition \ref{prp:swiss1} by exhibiting a filtration at the level of strict factorization algebras in our model of the $E_n$-center.

@@

Consider our factorization model for the $E_n$-enveloping algebra $\bU_n(\fg) = \clieu (\fg \otimes \Omega_c)$. 
The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra.

There is a similar filtration on our model for the $E_n$-center $\bZ_n(\fg)$. 
Define
\[
F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
\]

\brian{$\PP_0$ stuff}

@@

\begin{prp}
The pair $(\bZ_n (\fg), \bU_n(\fg)$ is a filtered, \brian{not sure what we're calling this}. 
Further, the associated graded $({\rm Gr} \; \bZ_n (\fg), {\rm Gr} \; \bU_n(\fg)$ is a $\PP_0$ \brian{not sure what we're calling this}. 
\end{prp}

It is immediate to check that this is a filtration of factorization algebras and that its associated graded has the structure of a $\PP_0$-factorization algebra.
In fact, we have the following result, which explains the relationship to the ``bulk" $(n+1)$-dimensional factorization algebra $\Tilde{\bZ}_n(\fg)$ we introduced in the last section.

 \begin{lmm}
Let $M$ be an $n$-dimensional manifold.
There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
\[
\pi_* \Tilde{\bZ}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
\]
where $\pi : M \times \RR_{>0} \to M$ is the projection. 
\end{lmm}

@@

\begin{dfn}\label{dfn:constructible1}
Let $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n(\fg))$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\Tilde{\bZ}_n (\fg)(U)$.
\item to an open set $U \subset M \times \RR_{\geq 0}$ with $U \cap (M \times \{0\}) \ne 0$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(U)$. 
\end{itemize}
\brian{not sure how much to say about structure maps}
\end{dfn}

It is immediate to check that this is a filtration of factorization algebras and that its associated graded has the structure of a $\PP_0$-factorization algebra.
In fact, we have the following result, which explains the relationship to the ``bulk" $(n+1)$-dimensional factorization algebra $\Tilde{\bZ}_n(\fg)$ we introduced in the last section.

 \begin{lmm}
Let $M$ be an $n$-dimensional manifold.
There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
\[
\pi_* \Tilde{\bZ}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
\]
where $\pi : M \times \RR_{>0} \to M$ is the projection. 
\end{lmm}

\begin{dfn}\label{dfn:constructible1}
Let $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n(\fg))$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\Tilde{\bZ}_n (\fg)(U)$.
\item to an open set $U \subset M \times \RR_{\geq 0}$ with $U \cap (M \times \{0\}) \ne 0$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(U)$. 
\end{itemize}
\brian{not sure how much to say about structure maps}
\end{dfn}

Let $M$ be an $n$-dimensional manifold and $\fg$ a Lie algebra.

\begin{dfn}
For an open set $U \subset M \times \RR_{>0}$ let $\Tilde{\bZ}_n(\fg) (U)$ be the cochain complex 
\[
\Tilde{\bZ}_n(\fg) (U) = \clie \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
\]
The assignment $\Tilde{\bZ}_n(\fg) (U)$ defines a locally constant factorization algebra on $M \times \RR_{>0}$. 
\end{dfn}

@@

\begin{prp}
$\Tilde{\bZ}_n(\fg)$ has the structure of a $\PP_0$-factorization algebra on $M \times \RR_{>0}$. 
\end{prp}
\begin{proof}
Note that as an underlying graded vector space $\Tilde{\bZ}_n(\fg) (U)$ is of the form
\[
{\rm Sym} \left(\fg^* \otimes \Bar{\Omega}_c (U) [n-1] \right) \; \Hat{\otimes} \; {\rm Sym}  \left(\fg \otimes \Omega_c(U) [2] \right)  .
\]
Let $x^* \otimes \alpha$ denote an element of $\fg \otimes \Bar{\Omega}_c (U)$ and $y \otimes \beta$ denote an element of $\fg \otimes \Omega_c(U) [2]$. 
Then, the bracket involving the linear elements $(x^* \otimes \alpha) \otimes 1$ and $1 \otimes (y \otimes \beta)$ is defined by
\begin{align*}
\{(x^* \otimes \alpha) \otimes 1 , 1 \otimes (y \otimes \beta)\} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
\{(x^* \otimes \alpha) \otimes 1 , (x'^* \otimes \alpha') \otimes 1\} & = 0 \\
\{1 \otimes (y \otimes \beta) , 1 \otimes (y' \otimes \beta')\} & = 0 . 
\end{align*}
Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms. 
The bracket is extended to the entire symmetric algebra by using the graded Leibniz rule.
\end{proof}

@@

\def \Fac {\mathrm{Fac}}
We now need to express the $E_n$-structure on ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, B_f)$ induced by the equivalence of Proposition~\ref{P:ModentoModSn}, and then on the subsequent isomorphic hom spaces of modules morphisms.  Since we are going to take advantage of the factorization algebra presentation of $\UU_n( \fg)$, see~Theorem~\ref{T:UnofLie}, we recall the following factorization algebra description of the centralizer.
Let $\cA \stackrel{f}\to \cB$ be a morphism of locally constant factorization algebras on $\RR^n$ corresponding to an $E_n$-algebra map similarly denoted. Then by Theorems~\ref{T:En=Fac}, \ref{T:centralizer=inthom} the centralizer of $f$ is represented by the locally constant factorization algebra  
${\rm Mor}_{\Fac_{\cA}}(\cA, \cB_f)$ which is the internal mapping object  of maps from $\cA$ to $\cB_f$ in the $\infty$-category of locally constant factorization algebras on $\RR^n$ which are a $\cA$-module.

>>>>

\begin{thm}
\label{thm:lurie1} 
There is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant prefactorization algebras on~$\RR^n$. 
\end{thm}

@@

Given an $\EE_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
This $\infty$-category is obtained by ``forgetting" the $\EE_{n+1}$-algebra to an $\EE_1$-algebra and then taking the left-modules for this $\EE_1$-algebra.

The operad of little $n$-disks is built from configurations of disjoint unions of $n$-disks inside $n$-dimensional Euclidean space.
The $(n+1)$-dimensional Swiss cheese operad is a two-colored operad whose algebras include pairs $(B, M)$ where $B$ is an $\EE_{n+1}$-algebra, $M$ is an $\EE_n$-algebra, and where $M$ is a left-module for $B$.

Geometrically, it is most constructive to view this operad as built from open sets in the upper half space $\HH^{n+1} = \{(x_1,\ldots, x_{n+1}) \; | \; x_{n+1} \geq 0\}$.
The colors include disks and half-disks. 
If one restricts to the ``disk" colors we recover the data of the $\EE_{n+1}$-algebra $B$. 
The operadic structure maps which include disks and half-disks embedded inside bigger half-disks encodes the left-module structure of $B$ on $M$.

The pair $(\fZ_{n} (A), A)$ can be given the structure of an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
In fact, $(\fZ_{n} (A), A)$ is the {\em universal} such pair in the sense that if $(B, A)$ is another such pair then there exists a unique (up to equivalence) map of $\EE_{n+1}$-algebras $B \to \fZ_n(A)$. 
This universality is a conjecture of \cite{Kontsevich} which was later made precise and proved in \cite{Thomas, Tamarkin, Dolgushev, jnkf others?}.

In this paper, we will use two models for algebras over the $(n+1)$-dimensional Swiss cheese operad. 
The first is obtained by considering pairs of locally constant factorization algebras on an $n$-dimensional manifold.

\begin{dfn}\label{dfn:pair}
A {\em factorization pair} on a manifold $M$ is a pair $(\bB, \bM)$ where
\begin{itemize}
\item $\bB$ is an $\EE_1$-algebra in locally constant factorization algebras;
\item $\bM$ is a locally constant factorization algebra together with map of $\EE_1$ factorization algebras $\bB \to \bZ_n(\bM)$.
\end{itemize}
\end{dfn}

An immediate consequence of Theorem \ref{thm:lurie1} and Theorem \ref{thm: centralizer} is that a factorization pair on $\RR^n$ determines an algebra over the $(n+1)$-dimensional Swiss cheese operad.

In the next section we will recall a different model for algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of constructible factorization algebras on $(n+1)$-dimensional manifolds with boundary.

@@

Given an $\EE_n$-algebra $A$, the pair $(\fZ_n (A) , A)$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
The first objective is to define a certain ``classical limit" of this pair in the case that $A$ is an $\EE_n$-enveloping algebra.

@@

The key insight is that there exists a filtration on our model for the $E_n$-center $\bZ_n(\fg)$ and the $E_n$-enveloping algebra $\bU_n (\fg)$ whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.

Given a filtered associative algebra whose associated graded is commutative, there exists a Poisson bracket on the associated graded algebra. 
If the associated graded of a filtered $\EE_n$-algebra is commutative, then it carries the structure of a $\PP_n$-algebra, which is similar to a Poisson algebra except the bracket is of cohomological degree $1-n$. 
There is a similar description of the ``classical limit"  of algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of algebras over a certain two-colored operad $\PP_{[n+1,n]}$, see \cite{Pavel1, Pavel2}. 
We recall the definition of this operad below.

@@

There is another geometric model \brian{finish}
The idea is too look at configurations of disks and half-disks inside of the upper-half space $\HH^{n+1} = \{(x_1,\ldots, x_{n+1}) \; | \; x_{n+1} \geq 0\}$. 
What results is a two-colored operad known as the $(n+1)$-dimensional Swiss cheese operad where the two colors correspond to disks and half-disks.

@@

A constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a pair of factorization algebras $(\pi_* \bA , \bA_{\partial})$ on $M$ which define a factorization pair as in Definition \ref{dfn:pair}.

The next goal of this section is to provide a model of the classical limit of the $\EE_n$-center as a constructible factorization algebra.

@@

We prove Proposition \ref{prp:swiss1} by exhibiting a filtration at the level of strict factorization algebras in our model of the $\EE_n$-center.

@@

Consider our factorization model for the $\EE_n$-enveloping algebra $\bU_n(\fg) = \clieu (\fg \otimes \Omega_c)$. 
The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra.

There is a similar filtration on our model for the $\EE_n$-center $\bZ_n(\fg)$ defined by
\[
F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
\]

Proposition \ref{prp:swiss1} is a direct consequence of the following lemma.

\begin{lmm}
These filtrations equip the pair $(\bZ_n (\fg), \bU_n(\fg))$ with the structure of a filtered \brian{name}.
Moreover, the associated graded pair $({\rm Gr} \; \bZ_n (\fg), {\rm Gr} \; \bU_n(\fg))$ is a commutative \brian{name}. 
\end{lmm}
\begin{proof}
One has
\[
{\rm Gr} \; \UU_n (\fg) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c [1] \right)
\]
and
\[
{\rm Gr} \; \bZ_n (\fg) = \clie^\bu\bigg(\fg \otimes \Omega^\bu \; , \; {\rm Sym} \left(\fg \otimes \Omega^\bu_c [1]\right) \bigg) 
\]
as factorization algebras. 
These are both commutative by direct inspection. 
\end{proof}

@@

We turn towards a model for the $\EE_n$-center as a constructible factorization algebra.

\begin{dfn}
For an open set $U \subset M \times \RR_{>0}$ let $\overset{\circ}{\bf Z}_n(\fg) (U)$ be the cochain complex 
\[
\overset{\circ}{\bf Z}_n(\fg) (U) = \clie \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
\]
The assignment $U \mapsto \overset{\circ}{\bf Z}_n(\fg) (U)$ defines a locally constant factorization algebra on $M \times \RR_{>0}$. 
\end{dfn}

 \begin{lmm}
Let $M$ be an $n$-dimensional manifold.
There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
\[
\pi_* \overset{\circ}{\bf Z}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
\]
where $\pi : M \times \RR_{>0} \to M$ is the projection. 
\end{lmm}

@@

\begin{dfn}\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\overset{\circ}{\bf Z}_n (\fg)(U)$.
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(V)$. 
\end{itemize}
\brian{not sure how much to say about structure maps}
\end{dfn}

@@

\begin{lmm}
$\bC_n(\fg)$ has the structure of a constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$. 
\end{lmm}
\begin{proof}
Note that as an underlying graded vector space $\Tilde{\bZ}_n(\fg) (U)$ is of the form
\[
{\rm Sym} \left(\fg^* \otimes \Bar{\Omega}_c (U) [n-1] \right) \; \Hat{\otimes} \; {\rm Sym}  \left(\fg \otimes \Omega_c(U) [2] \right)  .
\]
Let $x^* \otimes \alpha$ denote an element of $\fg \otimes \Bar{\Omega}_c (U)$ and $y \otimes \beta$ denote an element of $\fg \otimes \Omega_c(U) [2]$. 
Then, the bracket involving the linear elements $(x^* \otimes \alpha) \otimes 1$ and $1 \otimes (y \otimes \beta)$ is defined by
\begin{align*}
\{(x^* \otimes \alpha) \otimes 1 , 1 \otimes (y \otimes \beta)\} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
\{(x^* \otimes \alpha) \otimes 1 , (x'^* \otimes \alpha') \otimes 1\} & = 0 \\
\{1 \otimes (y \otimes \beta) , 1 \otimes (y' \otimes \beta')\} & = 0 . 
\end{align*}
Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms. 
The bracket is extended to the entire symmetric algebra by using the graded Leibniz rule.
\end{proof}

@@

\def \Fac {\mathrm{Fac}}
We now need to express the $E_n$-structure on ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, B_f)$ induced by the equivalence of Proposition~\ref{P:ModentoModSn}, and then on the subsequent isomorphic hom spaces of modules morphisms.  Since we are going to take advantage of the factorization algebra presentation of $\UU_n( \fg)$, see~Theorem~\ref{T:UnofLie}, we recall the following factorization algebra description of the centralizer.
Let $\cA \stackrel{f}\to \cB$ be a morphism of locally constant factorization algebras on $\RR^n$ corresponding to an $E_n$-algebra map similarly denoted. Then by Theorems~\ref{thm:lurie1}, \ref{T:centralizer=inthom} the centralizer of $f$ is represented by the locally constant factorization algebra  
${\rm Mor}_{\Fac_{\cA}}(\cA, \cB_f)$ which is the internal mapping object  of maps from $\cA$ to $\cB_f$ in the $\infty$-category of locally constant factorization algebras on $\RR^n$ which are a $\cA$-module.
